---
title: "Goal2VariablesOrganization"
author: "Jiayi Zhou"
date: "2022-12-09"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#read in y1 response variable file for later use
holder<- read.csv("holder.csv")
#remove extrac column
holder<-holder[,-1]
```

```{r}
#read in y2 response variable file for later use
holder2<- read.csv("holder2.csv")
#remove extrac column
holder2<-holder2[,-1]
```

this and following code work for crime rate variables
```{r}
#read in data for year 10, fill in missing space, and extract year 10 data
X10 <- read_excel("10.xlsx")
n <- nrow(X10)
a = 2
for( i in 1:(n/2)){
county <- X10$County[a]
X10$County[a-1] <- county
a = a + 2
}
n10 =subset(X10, Year =="2010")
```

```{r}
#read in data for year 11, fill in missing space, and extract year 11 data
X11 <- read_excel("11.xlsx")
n <- nrow(X11)
a = 2
for( i in 1:(n/2)){
county <- X11$County[a]
X11$County[a-1] <- county
a = a + 2
}
n11 =subset(X11, Year =="2011")
```

```{r}
#read in data for year 12, fill in missing space, and extract year 12 data
X12 <- read_excel("12.xlsx")
n <- nrow(X12)
a = 2
for( i in 1:(n/2)){
county <- X12$County[a]
X12$County[a-1] <- county
a = a + 2
}
n12 =subset(X12, Year =="2012")
```

```{r}
#read in data for year 13, fill in missing space, and extract year 13 data
X13 <- read_excel("13.xlsx")
n <- nrow(X13)
a = 2
for( i in 1:(n/2)){
county <- X13$County[a]
X13$County[a-1] <- county
a = a + 2
}
n13 =subset(X13, Year =="2013")
```

```{r}
#read in data for year 14, fill in missing space, and extract year 14 data
X14 <- read_excel("14.xlsx")
n <- nrow(X14)
a = 2
for( i in 1:(n/2)){
county <- X14$County[a]
X14$County[a-1] <- county
a = a + 2
}
n14 =subset(X14, Year =="2014")
```

```{r}
#read in data for year 15, fill in missing space, and extract year 15 data
X15 <- read_excel("15.xlsx")
n <- nrow(X15)
a = 2
for( i in 1:(n/2)){
county <- X15$County[a]
X15$County[a-1] <- county
a = a + 2
}
n15 =subset(X15, Year =="2015")
```

```{r}
#read in data for year 16, fill in missing space, and extract year 16 data
X16 <- read_excel("16.xlsx")
n <- nrow(X16)
a = 2
for( i in 1:(n/2)){
county <- X16$County[a]
X16$County[a-1] <- county
a = a + 2
}
n16 =subset(X16, Year =="2016")
```

```{r}
#read in data for year 17, fill in missing space, and extract year 17 data
X17 <- read_excel("17.xlsx")
n <- nrow(X17)
a = 2
for( i in 1:(n/2)){
county <- X17$County[a]
X17$County[a-1] <- county
a = a + 2
}
n17 =subset(X17, Year =="2017")
```

```{r}
#read in data for year 18, fill in missing space, and extract year 18 data
X18 <- read_excel("18.xlsx")
n <- nrow(X18)
a = 2
for( i in 1:(n/2)){
county <- X18$County[a]
X18$County[a-1] <- county
a = a + 2
}
n18 =subset(X18, Year =="2018")
```

```{r}
#read in data for year 19, fill in missing space, and extract year 19 data
X19 <- read_excel("19.xlsx")
n <- nrow(X19)
a = 2
for( i in 1:(n/2)){
county <- X19$County[a]
X19$County[a-1] <- county
a = a + 2
}
n19 =subset(X19, Year =="2019")
```

```{r}
#read in data for year 20, fill in missing space, and extract year 20, 21 data
X20 <- read_excel("20.xlsx")
n <- nrow(X20)
a = 2
for( i in 1:(n/2)){
county <- X20$County[a]
X20$County[a-1] <- county
a = a + 2
}
n20 =subset(X20, Year =="2020")
n21 =subset(X20, Year =="2021")
```

Combine all the data set by years, remove missing value, and rename variables
```{r}
#combine data
crimedata <- rbind(n10,n11,n12,n13,n14,n15,n16,n17,n18,n19,n20,n21)
#delete all the NAs in crimedata
crimedata <- subset(crimedata, crimedata$`Index Crime Rate` != '-')
crimedata<- crimedata[-c(3)]
crimedata<-crimedata[crimedata$Year!=2018,]#We are required to ignore the year 2018-2019 
#rename the variables
crimedata$County<- gsub('[0-9.]', '', crimedata$County)
crimedata$County<- gsub(',', '', crimedata$County)
```

modify holder file
```{r}
##Change holder's year into normal year, so we can merge holder with x later; holder is our y1 
holder$Group.1 <- ifelse(holder$Group.1 == 1011 , 2010, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1112 , 2011, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1213 , 2012, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1314 , 2013, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1415 , 2014, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1516 , 2015, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1617 , 2016, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1718 , 2017, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 1920 , 2019, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 2021 , 2020, holder$Group.1)
holder$Group.1 <- ifelse(holder$Group.1 == 2122 , 2021, holder$Group.1)
colnames(holder)<-c("Year","County","y1")
```

modify holder2 file
```{r}
###Change holder2's year into normal year, so we can merge holder2 with x later; holder2 is our y2
holder2$Group.1 <- ifelse(holder2$Group.1 == 1011 , 2010, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1112 , 2011, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1213 , 2012, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1314 , 2013, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1415 , 2014, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1516 , 2015, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1617 , 2016, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1718 , 2017, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 1920 , 2019, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 2021 , 2020, holder2$Group.1)
holder2$Group.1 <- ifelse(holder2$Group.1 == 2122 , 2021, holder2$Group.1)
colnames(holder2)<-c("Year","County","y2")
```

read in other explanatory variables
```{r}
#other explanatory variables by Xinyuan
Explanatory1<-read_excel("Explanatory1.xlsx")
```

merge the crime data with other explantory variables
```{r}
Combine<-merge(crimedata,Explanatory1,by.x=c("Year","County"),by.y=c("Year","County"))
```

start handle Ethnic make up variables
```{r}
#read in census data
census2010 <- read_excel("2010Census.xlsx")
census2020 <- read_excel("2020Census.xlsx")
labels2010 <- census2010$Label
labels2020 <- census2020$Label
census2010 <- census2010[,-1]
census2020 <- census2020[,-1]
```

```{r}
#select variables and add variable name
census2010 <-census2010[c(1,2,6),]
census2020 <-census2020[c(1,2,6),]
rownames(census2010) <- labels2010[c(1,2,6)]
rownames(census2020) <- labels2020[c(1,2,6)]
```

```{r}
#transform dataset for 2010
census2010 <- data.frame(census2010)
census2010 <- t(census2010)
census2010 <- data.frame(census2010)
census2010$County <- rownames(census2010)
rownames(census2010) <- 1:100
colnames(census2010) <- c("Total", "HispanicLatino" , "Black", "County")
```

```{r}
#modify county name
for( i in 1:100){
 census2010$County[i] <- unlist(strsplit( gsub('[[:punct:] ]+',',',census2010$County[i]), split = ","))[1]
}
```

```{r}
#transform dataset for 2020
census2020 <- data.frame(census2020)
census2020 <- t(census2020)
census2020 <- data.frame(census2020)
census2020$County <- rownames(census2020)
rownames(census2020) <- 1:100
colnames(census2020) <- c("Total", "HispanicLatino" , "Black", "County")
```

```{r}
#modify county name
for( i in 1:100){
 census2020$County[i] <- unlist(strsplit( gsub('[[:punct:] ]+',',',census2020$County[i]), split = ","))[1]
}
```

```{r}
#modify total, hispanic, black value for 2010
for( i in 1:100){
 census2010$Total[i] <- gsub('[[:punct:] ]+','',census2010$Total[i])
 census2010$HispanicLatino[i] <- gsub('[[:punct:] ]+','',census2010$HispanicLatino[i])
 census2010$Black[i] <- gsub('[[:punct:] ]+','',census2010$Black[i])
}
```

```{r}
#modify total, hispanic, black value for 2020
for( i in 1:100){
 census2020$Total[i] <- gsub('[[:punct:] ]+','',census2020$Total[i])
 census2020$HispanicLatino[i] <- gsub('[[:punct:] ]+','',census2020$HispanicLatino[i])
  census2020$Black[i] <- gsub('[[:punct:] ]+','',census2020$Black[i])
}
```

```{r}
#change type to numeric
census2010$Total <-as.numeric(census2010$Total)
census2020$Total <-as.numeric(census2020$Total)
census2010$HispanicLatino <-as.numeric(census2010$HispanicLatino)
census2020$HispanicLatino <-as.numeric(census2020$HispanicLatino)
census2010$Black <-as.numeric(census2010$Black)
census2020$Black <-as.numeric(census2020$Black)
```

```{r}
#calculated the difference
differencesTotal <- census2020$Total - census2010$Total
differencesHispanicLatino <- census2020$HispanicLatino - census2010$HispanicLatino
differencesBlack<- census2020$Black - census2010$Black
```

```{r}
#calculate the change
changeInTotal <- differencesTotal/10
changeInHispanicLatino<- differencesHispanicLatino/10
changeInBlack<- differencesBlack/10
```

```{r}
#add year o 2010 nd 2020
census2010$Year <- 2010
census2020$Year <- 2020
```

```{r}
#create static estiamtion for missing years
for( i in 1:9){
  Total = census2010$Total+i*changeInTotal
  HispanicLatino=census2010$HispanicLatino+i*changeInHispanicLatino
  Black=census2010$Black+i*changeInBlack
  assign(paste0("census201", i), data.frame(do.call(rbind, Map(data.frame, Total=Total, HispanicLatino=HispanicLatino, Black=Black, County=census2010$County, Year=(paste0("201", i))))))
}
```

```{r}
#bind all the census data
censusdata <- rbind(census2010,census2011,census2012,census2013,census2014,census2015,census2016,census2017,census2018,census2019,census2020)
```

```{r}
#newly merged data
Combine1<-merge(censusdata,Combine,by.x=c("Year","County"),by.y=c("Year","County"))
```

```{r}
#change county name to upper cases
Combine1$County = toupper(Combine1$County)
```

load in Political Views Data
```{r}
PoliticalViewsNCData <- read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/North Carolina Election Data.xlsx")
PoliticalViewsNCData2008 <- read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/PoliticalViewsNCData2008.xlsx")
PoliticalViewsNCData2012 <- read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/PoliticalViewsNCData2012.xlsx")
PoliticalViewsNCData2016 <- read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/PoliticalViewsNCData2016.xlsx")
PoliticalViewsNCData2020 <- read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/PoliticalViewsNCData2020.xlsx")
```

load in combine1 data, all explantory variable added
```{r}
Combine1<-read_excel("/deac/sta/classes/sta381-fa-2022/Team02/YifanAttempt/Combine_1_Updated.xlsx")
```

add y1
```{r}
#merge combine1--explanatory variable with Y1
Combine2<-merge(holder,Combine1,by.x=c("Year","County"),by.y=c("Year","County"))
```

add y2
```{r}
#Merge explanatory variable with Y2
Combine3<-merge(holder2,Combine1,by.x=c("Year","County"),by.y=c("Year","County"))
```

```{r}
#modify column names
colnames(Combine2) <- gsub(" ", "_", colnames(Combine2))
colnames(Combine3) <- gsub(" ", "_", colnames(Combine3))
Combine2$Property_Crime_Rate<- gsub(',', '', Combine2$Property_Crime_Rate)
Combine3$Property_Crime_Rate<- gsub(',', '', Combine3$Property_Crime_Rate)
```

```{r}
#change type of variables
Combine2$Violent_Crime_Rate <- as.numeric(Combine2$Violent_Crime_Rate)
Combine2$Property_Crime_Rate <- as.numeric(Combine2$Property_Crime_Rate)
Combine2$Defense_Counsel_Types <- as.numeric(Combine2$Defense_Counsel_Types)


Combine3$Violent_Crime_Rate <- as.numeric(Combine3$Violent_Crime_Rate)
Combine3$Property_Crime_Rate <- as.numeric(Combine3$Property_Crime_Rate)
Combine3$Defense_Counsel_Types <- as.numeric(Combine3$Defense_Counsel_Types)
```

```{r}
#Fix the missing values
Combine2[516, 8]<-3609.7
Combine2[610, 8]<-2855.2

Combine3[516, 8]<-3609.7
Combine3[610, 8]<-2855.2
```

```{r}
#change type of variables
Combine2$Judical_District_C <-as.factor(Combine2$Judical_District_C)
Combine2$Prosecutorial_District_B<-as.factor(Combine2$Prosecutorial_District_B)
```

```{r}
#discover correlation between variables
library(corrplot)
corrplot(cor(Combine2[c(1:909),c(4:10,13:15)]), type = "upper")
```

```{r}
#modify variables to change scale and break correlation
Combine2$HispanicLatino=Combine2$HispanicLatino/Combine2$Total
Combine2$Black=Combine2$Black/Combine2$Total
Combine2$Total=Combine2$Total/1000
Combine2$Volume_of_Cases_in_County=Combine2$Volume_of_Cases_in_County/Combine2$Total
```

```{r}
#modify variables to change scale and break correlation
Combine3$HispanicLatino=Combine3$HispanicLatino/Combine3$Total
Combine3$Black=Combine3$Black/Combine3$Total
Combine3$Total=Combine3$Total/1000
Combine3$Volume_of_Cases_in_County=Combine3$Volume_of_Cases_in_County/Combine3$Total
```

```{r}
write.csv(Combine2, file = "Combine2.csv")
write.csv(Combine3, file = "Combine3.csv")
```