---
title: "Map for Y2"
author: "YFL"
date: "2022-11-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---
title: "map test 2"
author: "yfl"
date: "2022-10-26"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning=FALSE, message=FALSE}
library(readxl)
#library(sf)
#library(raster)
library(dplyr)
library(spData)
#library(spDataLarge)
library(gridExtra)
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(ggplot2) # tidyverse data visualization package

```

```{r}
#importing all data for Y1
y2y1 <- read_excel("Y2's/y2y1.xlsx")
y2y2 <- read_excel("Y2's/y2y2.xlsx")
y2y3 <- read_excel("Y2's/y2y3.xlsx")
y2y4 <- read_excel("Y2's/y2y4.xlsx")
y2y5 <- read_excel("Y2's/y2y5.xlsx")
y2y6 <- read_excel("Y2's/y2y6.xlsx")
y2y7 <- read_excel("Y2's/y2y7.xlsx")
y2y8 <- read_excel("Y2's/y2y8.xlsx")
y2y9 <- read_excel("Y2's/y2y9.xlsx")
y2y10 <- read_excel("Y2's/y2y10.xlsx")
y2y11 <- read_excel("Y2's/y2y11.xlsx")
y2total <- read_excel("Y2's/y2 total rate.xlsx")
```

```{r, warning=FALSE, message=FALSE}
na.omit(y2y2)
na.omit(y2y3)
na.omit(y2y4)
na.omit(y2y5)
na.omit(y2y6)
na.omit(y2y7)
na.omit(y2y8)
na.omit(y2y9)
na.omit(y2y10)
na.omit(y2y11)
```

```{r}
y2y2$Count <- as.double(y2y2$Count)
y2y3$Count <- as.double(y2y3$Count)
y2y4$Count <- as.double(y2y4$Count)
y2y5$Count <- as.double(y2y5$Count)
y2y6$Count <- as.double(y2y6$Count)
y2y7$Count <- as.double(y2y7$Count)
y2y8$Count <- as.double(y2y8$Count)
y2y9$Count <- as.double(y2y9$Count)
y2y10$Count <- as.double(y2y10$Count)
y2y11$Count <- as.double(y2y11$Count)
```


Making the map for Y2's year 2010-2011

```{r, warning=FALSE, message=FALSE}
#map for y2y1
states <- map_data("state")
nc_df <- subset(states, region == "north carolina")
counties <- map_data("county")
nc_county <- subset(counties, region == "north carolina")


library(stringr)
    library(dplyr)

    # make a data frame
    x <- readLines("Y2's/y2y1.xlsx")
    pop_and_area <- str_match(x, "^([a-zA-Z ]+)County\t.*\t([0-9,]{2,10})\t([0-9,]{2,10}) sq mi$")[, -1] %>%
      na.omit() %>%
      str_replace_all(",", "") %>% 
      str_trim() %>%
      tolower() %>%
      as.data.frame(stringsAsFactors = FALSE)
      
    # give names and make population and area numeric
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )

cacopa <- read_excel("Y2's/y2y1.xlsx")
cacopa$subregion <-as.factor(cacopa$subregion)

#Makes NC
nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base


#Add y1 to the counties data set
for( i in 1:101){
  y2y1$subregion[i] <- tolower(y2y1$subregion[i])
}


nc_county_new <- merge(nc_county, y2y1, by = "subregion")

# Adds Counties
nc_base + labs(title = "Trial percent dispositions 2010-2011")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top
  theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
  
```

Making the map for Y1's year 2011-2012

```{r}
#map for y2y2
#Add y1 to the counties data set
for( i in 1:101){
  y2y2$subregion[i] <- tolower(y2y2$subregion[i])
}

nc_base<- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y2, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2011-2012")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2012-2013

```{r}
#map for y2y3
#Add y1 to the counties data set
for( i in 1:101){
  y2y3$subregion[i] <- tolower(y2y3$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y3, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2012-2013")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2013-2014

```{r}
#map for y2y4
#Add y1 to the counties data set
for( i in 1:101){
  y2y4$subregion[i] <- tolower(y2y4$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y4, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2013-2014")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```


Making the map for Y1's year 2014-2015

```{r}
#map for y2y5
#Add y1 to the counties data set
for( i in 1:101){
  y2y5$subregion[i] <- tolower(y2y5$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y5, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2014-2015")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2015-2016

```{r}
#map for y2y6
#Add y1 to the counties data set
for( i in 1:101){
  y2y6$subregion[i] <- tolower(y2y6$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y6, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2015-2016")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2016-2017

```{r}
#map for y2y7
#Add y1 to the counties data set
for( i in 1:101){
  y2y7$subregion[i] <- tolower(y2y7$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y7, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2016-2017")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2017-2018

```{r}
#map for y2y8
#Add y1 to the counties data set
for( i in 1:101){
  y2y8$subregion[i] <- tolower(y2y8$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y8, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2017-2018")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2019-2020

```{r}
#map for y2y9
#Add y1 to the counties data set
for( i in 1:101){
  y2y9$subregion[i] <- tolower(y2y9$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y9, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2019-2020")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```


Making the map for Y1's year 2020-2021

```{r}
#map for y2y10
#Add y1 to the counties data set
for( i in 1:101){
  y2y10$subregion[i] <- tolower(y2y10$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y10, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2020-2021")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

Making the map for Y1's year 2021-2022

```{r}
#map for y2y11
#Add y1 to the counties data set
for( i in 1:101){
  y2y11$subregion[i] <- tolower(y2y11$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y2y11, by = "subregion")

nc_base + labs(title = "Trial percent dispositions 2021-2022")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
```

```{r}
#map for y1 total rate
#Add y1 to the counties data set
for( i in 1:101){
  y2total$subregion[i] <- tolower(y2total$subregion[i])
}
y2total$Count <- y2total$`Total per county`

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")

nc_county_new <- merge(nc_county, y2total, by = "subregion")

nc_base + labs(title = "Total Trial percent dispositions 2010-2021")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(20)),
                         limit=range(0,1))
```


