---
title: "Map for Y1"
author: "YFL"
date: "2022-11-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---
title: "map test 2"
author: "yfl"
date: "2022-10-26"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning=FALSE, message=FALSE}
library(readxl)
#library(sf)
#library(raster)
library(dplyr)
library(spData)
#library(spDataLarge)
library(gridExtra)
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(ggplot2) # tidyverse data visualization package

```

```{r}
#importing all data for Y1
y1y1 <- read_excel("Y1's/y1y1.xlsx")
y1y2 <- read_excel("Y1's/y1y2.xlsx")
y1y3 <- read_excel("Y1's/y1y3.xlsx")
y1y4 <- read_excel("Y1's/y1y4.xlsx")
y1y5 <- read_excel("Y1's/y1y5.xlsx")
y1y6 <- read_excel("Y1's/y1y6.xlsx")
y1y7 <- read_excel("Y1's/y1y7.xlsx")
y1y8 <- read_excel("Y1's/y1y8.xlsx")
y1y9 <- read_excel("Y1's/y1y9.xlsx")
y1y10 <- read_excel("Y1's/y1y10.xlsx")
y1y11 <- read_excel("Y1's/y1y11.xlsx")
y1total <- read_excel("Y1's/y1 total rate.xlsx")
```



Making the map for Y1's year 2010-2011

```{r, warning=FALSE, message=FALSE}
#map for y1y1
states <- map_data("state")
nc_df <- subset(states, region == "north carolina")
counties <- map_data("county")
nc_county <- subset(counties, region == "north carolina")


library(stringr)
    library(dplyr)

    # make a data frame
    x <- readLines("Y1's/y1y1.xlsx")
    pop_and_area <- str_match(x, "^([a-zA-Z ]+)County\t.*\t([0-9,]{2,10})\t([0-9,]{2,10}) sq mi$")[, -1] %>%
      na.omit() %>%
      str_replace_all(",", "") %>% 
      str_trim() %>%
      tolower() %>%
      as.data.frame(stringsAsFactors = FALSE)
      
    # give names and make population and area numeric
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )

cacopa <- read_excel("Y1's/y1y1.xlsx")
cacopa$County <-as.factor(cacopa$County)
#table(cacopa$County)

#Makes NC
nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base


#Add y1 to the counties data set
for( i in 1:101){
  y1y1$County[i] <- tolower(y1y1$County[i])
}

# Change the column names to match
colnames(y1y1)[1] <- "subregion"

nc_county_new <- merge(nc_county, y1y1, by = "subregion")

# Adds Counties
p1<- nc_base + labs(title = "Trial rate percent convictions 2010-2011")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top
  theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p1
```

Making the map for Y1's year 2011-2012

```{r}
#map for y1y2
#Add y1 to the counties data set
for( i in 1:101){
  y1y2$subregion[i] <- tolower(y1y2$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new2 <- merge(nc_county, y1y2, by = "subregion")

p2<-nc_base + labs(title = "Trial rate percent convictions 2011-2012")+
  geom_polygon(data = nc_county_new2, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p2
```

Making the map for Y1's year 2012-2013

```{r}
#map for y1y3
#Add y1 to the counties data set
for( i in 1:101){
  y1y3$subregion[i] <- tolower(y1y3$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new3 <- merge(nc_county, y1y3, by = "subregion")

p3<-nc_base + labs(title = "Trial rate percent convictions 2012-2013")+
  geom_polygon(data = nc_county_new3, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p3
```

Making the map for Y1's year 2013-2014

```{r}
#map for y1y4
#Add y1 to the counties data set
for( i in 1:101){
  y1y4$subregion[i] <- tolower(y1y4$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new4 <- merge(nc_county, y1y4, by = "subregion")

p4<-nc_base + labs(title = "Trial rate percent convictions 2013-2014")+
  geom_polygon(data = nc_county_new4, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p4
```


Making the map for Y1's year 2014-2015

```{r}
#map for y1y5
#Add y1 to the counties data set
for( i in 1:101){
  y1y5$subregion[i] <- tolower(y1y5$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new5 <- merge(nc_county, y1y5, by = "subregion")

p5<-nc_base + labs(title = "Trial rate percent convictions 2014-2015")+
  geom_polygon(data = nc_county_new5, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p5
```

Making the map for Y1's year 2015-2016

```{r}
#map for y1y6
#Add y1 to the counties data set
for( i in 1:101){
  y1y6$subregion[i] <- tolower(y1y6$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new6 <- merge(nc_county, y1y6, by = "subregion")

p6<-nc_base + labs(title = "Trial rate percent convictions 2015-2016")+
  geom_polygon(data = nc_county_new6, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p6
```

Making the map for Y1's year 2016-2017

```{r}
#map for y1y7
#Add y1 to the counties data set
for( i in 1:101){
  y1y7$subregion[i] <- tolower(y1y7$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new7 <- merge(nc_county, y1y7, by = "subregion")

p7<-nc_base + labs(title = "Trial rate percent convictions 2016-2017")+
  geom_polygon(data = nc_county_new7, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p7
```

Making the map for Y1's year 2017-2018

```{r}
#map for y1y8
#Add y1 to the counties data set
for( i in 1:101){
  y1y8$subregion[i] <- tolower(y1y8$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new8 <- merge(nc_county, y1y8, by = "subregion")

p8<-nc_base + labs(title = "Trial rate percent convictions 2017-2018")+
  geom_polygon(data = nc_county_new8, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p8
```

Making the map for Y1's year 2019-2020

```{r}
#map for y1y9
#Add y1 to the counties data set
for( i in 1:101){
  y1y9$subregion[i] <- tolower(y1y9$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new9 <- merge(nc_county, y1y9, by = "subregion")

p9<-nc_base + labs(title = "Trial rate percent convictions 2019-2020")+
  geom_polygon(data = nc_county_new9, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p9
```


Making the map for Y1's year 2020-2021

```{r}
#map for y1y10
#Add y1 to the counties data set
for( i in 1:101){
  y1y10$subregion[i] <- tolower(y1y10$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new10 <- merge(nc_county, y1y10, by = "subregion")

p10<-nc_base + labs(title = "Trial rate percent convictions 2020-2021")+
  geom_polygon(data = nc_county_new10, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p10
```

Making the map for Y1's year 2021-2022

```{r}
#map for y1y11
#Add y1 to the counties data set
for( i in 1:101){
  y1y11$subregion[i] <- tolower(y1y11$subregion[i])
}

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new11 <- merge(nc_county, y1y11, by = "subregion")

p11<-nc_base + labs(title = "Trial rate percent convictions 2021-2022")+
  geom_polygon(data = nc_county_new11, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(0,0.03,0.06,0.09,0.12), limit=range(0,.15))
p11
```

```{r}
#map for y1 total rate
#Add y1 to the counties data set
for( i in 1:101){
  y1total$subregion[i] <- tolower(y1total$subregion[i])
}
y1total$Count <- y1total$`Total per county`

nc_base <- ggplot(data = nc_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
#nc_base

nc_county_new <- merge(nc_county, y1total, by = "subregion")

ptotal<-nc_base + labs(title = "Total trial rate percent convictions")+
  geom_polygon(data = nc_county_new, aes(fill = Count), color = "white") +
  geom_polygon(color = "black", fill = NA) +   # get the state border back on top+
      theme_bw()+
   scale_fill_gradientn(colours = rev(rainbow(20)),
                         limit=range(0,1))
ptotal
```


